---
title: "MATE6611_Project"
author: ""
date: "9/25/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 4.2


```{r include=FALSE}
X <- c(3.36, 2.88, 3.63, 3.41, 3.78, 4.02, 4.00, 4.23, 3.73, 3.85, 3.97, 4.51, 4.54, 5.00, 5.00, 4.72, 5.00)

Y <- c(65, 156, 100, 134, 16, 108, 121, 4, 39, 143, 56, 26, 22, 1, 1, 5, 65)

plot(X,Y)

cor(X,Y)
```





### c Show that $\mathbb{E}[Y] = \frac{1}{\theta}$ and that $Var(Y) = \frac{1}{\theta^2}$

Calculating the mean:

\[ \mathbb{E}[Y] = \int_0^{\infty} y \theta e^{-y\theta} dy \]
Using integration by parts, let $u=y$, $dv = \theta e^{-y\theta dy}$, then

\[\mathbb{E}[Y] = -ye^{-y\theta} \biggr\rvert_{0}^{\infty} + \int_0^{\infty}e^{-e\theta} dy = 0 + \frac{-e^{-y\theta}}{\theta}\biggr\rvert_{0}^{\infty} = \frac{1}{\theta}\]

Calculating variance:

\[Var(Y) = \mathbb{E}[Y^2] - \mathbb{E}[Y]^2 = \int_0^{\infty}y^2\theta e^{-y\theta} dy - \theta^{-2}  \]
Using integration by parts, let $u = y^2$ and $dv = \theta e^{-y\theta} dy$, then

\[Var(Y) = -y^2 e^{-y\theta}\biggr\rvert_0^{\infty} + 2\int_0^{\infty} y e^{-y\theta} dy - \theta^{-2} = -\frac{1}{\theta^2} + \frac{2}{\theta} \int_0^{\infty} y\theta e^{-y\theta} dy = -\frac{1}{\theta^2} + \frac{2}{\theta}\mathbb{E}[Y] = -\frac{1}{\theta^2} + \frac{2}{\theta^2} = \frac{1}{\theta^2} \]


